Data Preparation

### 2019-03-11 Data Preparation.Rmd

@@

# Extra

## Extracting Descriptions

# Setup
symbol_to_line <- c("\r\n", "\n") %>%
  paste(collapse = "|")
start_descrip <- c("^Description", "^Course Description") %>%
  paste(collapse = "|")
end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
  paste(collapse = "|")

# Loop
for(course in 1 : nrow(d_description)){

  overview <- d_description$Overview[course]

  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
  # for overviews w/o Literature section, find section Instructional Format.
  if(is_empty(line_end)){
    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
    print(paste("line_end irregular for", d_description$`Course ID`[course],
                "in catalogue", d_description$`Calendar Year`[course]))
    } # close if-statement

  description <- paste(overview_by_line[line_start : line_end], collapse = " ")

  d_description$Description[course] <- description

}
rm(symbol_to_line, start_descrip, end_descrip,
   course, overview, overview_by_line, line_start, line_end, description)
print(d_description)
```

>>>>

##### Extracting Descriptions

# Setup
symbol_to_line <- c("\r\n", "\n") %>% paste(collapse = "|")
start_descrip  <- c("^Description", "^Course Description") %>% paste(collapse = "|")
end_descrip    <- c("^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all") %>%  paste(collapse = "|")

# helper functions
split              <- function(string) string %>% str_split(pattern = "\r\n|\n")

is_start_descrip   <- function(x) x %>% str_detect(pattern = start_descrip           )
is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )
is_end_descrip_bis <- function(x) x %>% str_detect(pattern = "^Instructional format$")

# main function
extract_description <- function(page){

  page %>%
    split %>%
    tibble(line = .) %>%

    mutate(
      is_start_descrip = line %>% is_start_descrip,
      is_end_descrip   = line %>% is_end_descrip
    ) %>%

    mutate(
      is_end_descrip = if_else(any(is_end_descrip), is_end_descrip, line %>% is_end_descrip_bis)
    ) %>%

    # filter the description section
    mutate(
      is_after_start_descrip = cumany( is_start_descrip),
      is_before_end_descrip  = cumall(!is_end_descrip  ),
      is_descrip             = is_after_start_descrip & is_before_end_descrip
      ) %>%
    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%

    summarise(description = str_c(line, collapse = " ")) %>%
    pull

d_text$overview %>%
  mutate(
    description = overview %>% map(extract_description)
  )
```

@@
